```{r "intro"}
#| echo: false
intro <- tryCatch(
    {
        description <- packageDescription("YESCDSbook")
        pkg <- description$Package
        version <- description$Version
        authors <- eval(parse(text = description$Authors))
        license <- description$License
        glue::glue(
            "**Package:** {pkg}<br/>\n", 
            "**Authors:** {paste(format(authors, include = c('given', 'family', 'role')), collapse = ', ')}<br/>\n", 
            "**Compiled:** {as.character(Sys.Date())}<br/>\n", 
            "**Package version:** {version}<br/>\n", 
            "**R version:** <b style='color:red;'>{R.version.string}</b><br/>\n", 
            "**BioC version:** <b style='color:red;'>{BiocManager::version()}</b><br/>\n", 
            "**License:** {license}<br/>"
        )
    }, 
    error = function(e) {"Local preview"}
)
```

`r intro`

# Welcome {-}

This is the landing page of the `BiocBook` entitled "Cancer data science concepts for undergraduates"

This book introduces the reader to the concepts mapped below:

[coggle](https://github.com/vjcitn/YESCDS/blob/main/Cancer_Data_Science_Topics.png?raw=true)

The [YESCDS R package](https://github.com/vjcitn/YESCDS) includes
data structures and functions used in this book.


# Docker image {-}

A `Docker` image built from this repository is available here: 

👉 [ghcr.io/vjcitn/yescdsbook](https://ghcr.io/vjcitn/yescdsbook) 🐳

::: {.callout-tip icon='true'}
## Get started now 🎉

You can get access to all the packages used in this book in < 1 minute, 
using this command in a terminal: 

```{sh "docker", filename="bash"}
#| eval: false
docker run -it ghcr.io/vjcitn/yescdsbook:devel R
```

:::

# RStudio Server {-}

An RStudio Server instance can be initiated from the `Docker` image as follows: 

```{sh "rstudio", filename="bash"}
#| eval: false
docker run \
    --volume <local_folder>:<destination_folder> \
    -e PASSWORD=OHCA \
    -p 8787:8787 \
    ghcr.io/vjcitn/yescdsbook:devel
```

The initiated RStudio Server instance will be available at 
[https://localhost:8787](https://localhost:8787).

<!-- 
# System dependencies and conda 

A pre-configured `micromamba` environment called `BiocBook` is available 
once the Docker image is loaded. It provides all the softwares listed in 
`requirements.yml`. 

```{sh "micromamba", filename="bash"}
#| eval: false
docker run -it ghcr.io/vjcitn/yescdsbook:devel bash
micromamba activate BiocBook
``` 
-->


# Acknowledgments {-}

Contributors: 

- Alexandru Mahmoud, Channing Division of Network Medicine, Mass General Brigham
- Brittany Michel, Dana-Farber Cancer Institute
- Latrice Landry, Perelman School of Medicine, University of Pennsylvania
- Karen Burns White, Dana-Farber Cancer Institute
- Vincent Carey, Channing Division of Network Medicine, Mass General Brigham

This project is supported in part by

- NSF ACCESS Allocation BIR190004 "Engineering and disseminating a software and analysis ecosystem for genomic data science"

- Chan-Zuckerberg Initiative EOSS Diversity & Inclusiveness EOSS-DI-0000000033 "Bioconductor: Sustaining a Worldwide Community of Genome Data Scientists"

- National Cancer Institute 5U24CA180996-08 "Cancer Genomics: Integrative and Scalable Solutions in R/Bioconductor"

- National Human Genome Research Institute 2U24HG004059-17 "Bioconductor: An Open-Source, Open-Development Computing Resource for Genomics"


# Session info {-}

::: {.callout-note collapse="true"}

## Click to expand 👇

```{r "session info"}
#| cache: false
sessioninfo::session_info(
    installed.packages()[,"Package"], 
    include_base = TRUE
)
```

:::
